Wide binaries in Gaia DR1

### 2016-09-28 paper/ms.tex
tweak

% define macros for math
\newcommand{\given}{\,|\,}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\transp}[1]{{#1}^{\mathsf{T}}}
\newcommand{\inv}[1]{{#1}^{-1}}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\newcommand{\vperp}{\bs{v}^\perp}
\newcommand{\propm}{\bs{\mu}}
\newcommand{\matrx}[1]{\mathbf{#1}}
\newcommand{\kms}{\rm km~s^{-1}}

@@

>>>>

% define macros for math
\newcommand{\given}{\,|\,}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\transp}[1]{{#1}^{\!\mathsf{T}}}
\newcommand{\inv}[1]{{#1}^{-1}}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\newcommand{\vperp}{\bs{v}^\perp}
\newcommand{\propm}{\bs{\mu}}
\newcommand{\matrx}[1]{\mathbf{#1}}
\newcommand{\kms}{\rm km~s^{-1}}

@@

\appendix
\section{Some mathematics relevant to the above}

In what follows, all vectors are column vectors.
Properties of the squared exponential:
\begin{eqnarray}
  \ln\left[\int\exp(-\frac{1}{2}\,[x-\mu]\transp\,A\inv\,[x-\mu] - \Delta)\,\dd x\right]
  &=& -\frac{d}{2}\,\ln 2\pi -\frac{1}{2}\ln ||A|| -\Delta
  \quad ,
\end{eqnarray}
where $x$ and $\mu$ are $d$-dimensional vectors, $A$ is a symmetric
matrix, $\Delta$ is a scalar, and the integral is implicitly over all
of $d$-space.
We will need to complete squares.
If we equate
\begin{eqnarray}
  \frac{1}{2}\,[x-\mu]\transp\,A\inv\,[x-\mu] + \Delta
  &=& \frac{1}{2}\,x\transp\,A\inv\,x + x\transp\,B\,b + C
  \quad ,
\end{eqnarray}
where $B\,b$ is a $d$-vector, and $C$ is a scalar, then we find
\begin{eqnarray}
  \mu &=& A\,B\,b
  \\
  C & = & \Delta - \frac{1}{2}\,\mu\transp\,A\inv\,\mu
  \quad .
\end{eqnarray}

Now in this case, we want to write down the probability of the
